\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Divik Chotani} \\ \vspace{1pt}
    \small 408-726-2484 $|$ \href{mailto:divikchotani@g.ucla.edu}{\underline{divikchotani@g.ucla.edu}} $|$ 
    \href{https://www.linkedin.com/in/divik-chotani-8b3585242/}{\underline{LinkedIn}} $|$
    \href{https://github.com/DivikChotani}{\underline{GitHub}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    % Swap to: position=degree, date=duration, institution, location
    \resumeSubheading
      {Bachelor of Engineering in Computer Science}{Oct. 2023 -- June 2027}
      {University of California, Los Angeles}{Los Angeles, CA}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

 \resumeSubheading
  {Undergraduate Research Assistant}{Mar. 2025 -- Present}
  {UCLA, Samueli School of Engineering}{Los Angeles, CA}
\resumeItemListStart
  \resumeItem{Contributed to the open-source \href{https://github.com/binpash/pash}{\underline{PaSh}} project (500+ stars, hosted by the Linux Foundation), by implementing parallel versions of core POSIX commands and submitting enhancements to its compiler optimization passes.}
  \resumeItem{Actively maintained PaSh’s open-source \href{https://github.com/binpash/annotations}{\underline{annotations}} library, extending its semantics and dependency-tracking capabilities to allow users to parallelize their own custom commands while maintaining correctness.}
  \resumeItem{Created an eBPF program in C, C++, and Rust to monitor system calls, interrupts, and network packets on Linux, enabling dependency tracking and file access auditing.}
\resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{Sep. 2024 -- Jan. 2025}
      {Validia}{San Francisco, CA}
    \resumeItemListStart
      \resumeItem{Developed a Chrome extension using React and Node.js to protect websites via facial authentication.}
      \resumeItem{Created a web app in raw HTML, CSS, and JavaScript with a Flask backend to detect deepfake videos in interviews.}
      \resumeItem{Boosted audio deepfake detection accuracy by 20\% (measured on 1,000+ audio samples) using PyTorch.}
      \resumeItem{Implemented a Fast Fourier Transform (FFT) to extract frequency-domain features from audio clips, improving detection performance.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{June 2024 -- Sept. 2024 \& June 2025 -- Sept. 2025}{Pixii AI}{Boston, MA}
    \resumeItemListStart
      \resumeItem{June 2024 -- Sept. 2024: Developed a Slackbot with Nest.js and PostgreSQL to generate 30 days of AI-powered ad content in under 30 seconds, automating marketing across 50+ social media accounts.}
      \resumeItem{June 2025 -- Sept. 2025: Built a social media scheduler in TypeScript using React, Nest.js, and Docker to plan and publish posts, greatly reducing manual marketing workload.}
      \resumeItem{June 2025 -- Sept. 2025: Implemented a usage tracker with PostHog, Next.js, and Node.js to analyze user behavior and inform UI improvements, boosting user return rate to 24\%.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\begin{tabular}[t]{@{}l@{}}%
  \textbf{Co-op Minesweeper} $|$ \emph{TypeScript, Node.js, React, PostgreSQL, Docker} \\
  \href{https://coopminesweeper.netlify.app/game}{\underline{Link to the website}}%
\end{tabular}}{June 2024 -- Dec. 2024}
\resumeItemListStart
  \resumeItem{Developed a full-stack web application with Node.js serving a REST API and React frontend for seamless gameplay and user management.}
  \resumeItem{Implemented secure authentication with hashed and salted passwords; integrated a PostgreSQL database to store user profiles, scores, and game history.}
  \resumeItem{Leveraged Socket.io to enable real-time multiplayer functionality, allowing multiple players to collaborate on the same Minesweeper board with instant updates.}
\resumeItemListEnd

\resumeProjectHeading
{\begin{tabular}[t]{@{}l@{}}%
  \textbf{Amazon Listing Grader} $|$ \emph{TypeScript, Node.js, React, SQLite3} \\
  \href{https://main.d26yxwj97blw7k.amplifyapp.com/}{\underline{Link to project website}}%
\end{tabular}}{June 2025 -- Sept. 2025}
\resumeItemListStart
  \resumeItem{Built a web app to evaluate and score product listings for any Amazon product where a user inputs a product url and the website scores the product listing and provides insight on how to improve listing.}
  \resumeItem{Created a responsive React frontend to present AI-powered reviews and suggestions, as well detailed analysis.}
  \resumeItem{Implemented a Node.js backend with Postgres and deployed via AWS Amplify to allow for continuous deployment and API Gateway for  communication between the frontend and backend.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++/C\#, SQL, JavaScript, HTML/CSS, Rust, Go, BPF, Swift, Kotlin} \\
     \textbf{Frameworks}{: React, Next.js, Node.js, Flask, WordPress, Material-UI, Tailwind, FastAPI, Vue.js, Svelte, Angular, Django, .NET, Spring Boot} \\
     \textbf{Developer Tools}{: Git, Docker, Google Cloud Platform, MongoDB, Redis, DynamoDB, GraphQL, bpftool} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, scikit-learn, PyTorch, libbpf, linux-headers, Axios, Vite, TypeORM, Socket.io}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
